\section{Preliminaries}
\subsection{CFG}
A control flow graph (CFG) in computer science is a representation, using graph notation, of all paths that might be traversed through a program during its execution.
In a control flow graph each node in the graph represents a basic block, i.e. a straight-line piece of code without any jumps or jump targets; jump targets start a block, and jumps end a block. Directed edges are used to represent jumps in the control flow. There are, in most presentations, two specially designated blocks: the entry block, through which control enters into the flow graph, and the exit block, through which all control flow leaves.

\subsection{SPF}
Symbolic PathFinder (SPF) \cite{spf} combines symbolic execution with model checking and constraint solving for test case generation. In this tool, programs are executed on symbolic inputs representing multiple concrete inputs. Values of variables are represented as numeric constraints, generated from analysis of the code structure. These constraints are then solved to generate test inputs guaranteed to reach that part of code. Essentially SPF performs symbolic execution for Java programs at the bytecode level. Symbolic PathFinder uses the analysis engine of the Ames JPF model checking tool (i.e. jpf-core) \cite{jpf}.


\subsection{Veritesting}
Veritesting\cite{veritesting} is a technique that reduces the number of paths that need to be explored by avoiding unnecessary forking. 
%
Veritesting identifies regions of if-statements that can be statically explored and captured in a logical formula (usually as disjunction of formulas representing different branches in if-statement). 
%
We will call this formula VeriFormula which captures possible different execution paths. 
%
The result of this process is a VeriFormula, which can be submitted to a SMT solver. 
%
If the formula is satisfiable, then there is some path through the code region that reaches the exit point. In this case, dynamic symbolic execution is resumed after updating the PC with the VeriFormula and also updating symbolic values of variable if needed. 
